### 2018-08-06 paper/intro.tex
Updates contributions

Constructing a system that provides fully anonymous content sharing while avoiding the above pitfalls is unfortunately highly
challenging. The last two decades have witnessed many attempts at building privacy-preserving and anonymous P2P data-sharing
networks~\cite{Clarke:2001,Gnunet2002,Freedman:2002,Nambiar:2006,Rennhard:2002}.
These solutions typically leverage \emph{onion
 routing}~\cite{Chaum:1981}, with some improvements to perform node
 discovery in a distributed manner, a step that is otherwise
centralized in traditional onion routing schemes. However, because of the high
churn typically experienced by P2P networks, the performance of these systems has been
discouraging~\cite{LeBlond:2013}; churn causes routes to disappear and be
reconstructed frequently, which is particularly costly. By contrast, Tor
\cite{Dingledine:2004}, one of the most popular anonymous networks,
trades lower anonymity guaranties for a much better performance. Tor's lower protection arises from
a partially centralized design that hinges on a set of \emph{directory
servers}, which are used to advertise trusted nodes that are available to bootstrap onion
routes.

@@

Our contributions are as follows: 
\begin{itemize}
\item We have designed \name, a novel fully decentralized, autonomous,
and self-organizing file sharing service among users based on a novel
concept named Probabilistic Onion Routes (POR), which combines onion routing with
probabilistic node selection, informed by random peer sampling and
Hidden Markov Model predictions for node availability;
\item  We have demonstrated the successfulness of our approach. Even
  suboptimal prediction results in successful file transfer with high
  probability. 
\end{itemize}

>>>>

Constructing a system that provides fully anonymous content sharing while avoiding the above pitfalls is unfortunately highly
challenging. The last two decades have witnessed many attempts at building privacy-preserving and anonymous P2P data-sharing
networks~\cite{Clarke:2001,Gnunet2002,Freedman:2002,Nambiar:2006,Rennhard:2002}.
These solutions typically leverage \emph{onion
 routing}~\cite{Chaum:1981}, with some improvements to perform node
 discovery in a distributed manner, a step that is otherwise
centralized in traditional onion routing schemes. However, because of the high
churn typically experienced by P2P networks, the performance of these systems has been
discouraging~\cite{LeBlond:2013}; churn causes routes to disappear and be
reconstructed frequently, which is particularly costly. By contrast, Tor
\cite{Tor}, one of the most popular anonymous networks,
trades lower anonymity guaranties for a much better performance. Tor's lower protection arises from
a partially centralized design that hinges on a set of \emph{directory
servers}, which are used to advertise trusted nodes that are available to bootstrap onion
routes.

@@

Our contributions are as follows: 
\begin{itemize}
  \item We provide the Sphinxes mix-header format which extends 
    Sphinx~\cite{Sphinx} to a source-routed limited random-walk protocol --- 
    \ie each layer of the onion route contains several alternative next nodes.

  \item We provide the \ac{SPOR} node selection strategy which, given a secure 
    \ac{RPS} protocol and availability estimates, selects nodes to populate the 
    layers of Sphinxes to maximize the availability of the route --- this 
    yields reliable routes even with low-availability nodes.

  \item We provide a protocol for a device swarm to estimate the availabilities 
    of its own devices.
    These availabilities can then be used with \ac{SPOR}.
    \commentDaniel{We should add some more details, maybe.}

  \item We use \ac{SPOR} to design \name: a novel, fully decentralized, 
    autonomous and self-organizing file transfer service among users.
\end{itemize}
